### 2018-07-10 dissertation/5-simulations/chapter5.tex
updated conclusion

Most of the parameters for the ONE simulator were taken from the article detailing the Working Day Movement Model \citep{ekman2008working}; the most important parameters are shown in \Cref{table:parameters}.
The simulation ran for 86400 seconds (24 hours), with a work day length of 28800 seconds (8 hours) and a standard deviation of departure time of 7200 seconds (2 hours).
Nodes move between 7 and 10 m/s in an area of approximately 14.7 km\textsuperscript{2} based on a section of the map of Helsinki.
%The number of nodes and their communication range vary for different simulations.
There is a total of 160 nodes, 150 of which follow the Working Day Movement Model, and 10 that follow the random waypoint mobility model to simulate vehicles that do not follow daily patterns.
Since this simulation is for vehicles instead of pedestrians, there are no buses in the model and every node is guaranteed to own a vehicle and travel by car.
Aside from the office size parameter, the parameters regarding offices, meeting spots and shopping were kept intact.
A small part of nodes move randomly to simulate vehicles that do not follow daily patterns.
The transmission range of nodes varies from simulation to simulation, for reasons explained in \Cref{section:density}.

@@

\pagebreak
\Cref{fig:randommalicious1} and \Cref{fig:randommalicious2} show the variation of results for different amounts of malicious nodes in the network.
By the end of one day, the algorithm is able to detect all malicious nodes when they are up to 30\% of the network, although there is still a small amount of false positive detections.
At 40\%, a small part of malicious nodes are yet to be detected and the standard deviation is larger overall.
At 50\%, as expected, the results are inconsistent as the network is completely split between benign and malicious nodes; at this point, the network is considered completely compromised.
True positive and false positive detections are often inverted, because whenever there are more malicious nodes than benign one in a certain node's network model, the algorithm will classify the malicious ones as correct.
The amount of malicious nodes also affects how quickly nodes are able to acquire information about the network, since nodes do not trust information from malicious neighbors.

>>>>

Most of the parameters for the ONE simulator were taken from the article detailing the Working Day Movement Model \citep{ekman2008working}; the most important parameters are shown in \Cref{table:parameters}.
The simulation ran for 86400 seconds (24 hours), with a work day length of 28800 seconds (8 hours) and a standard deviation of departure time of 7200 seconds (2 hours).
Nodes move between 7 and 10 m/s in an area of approximately 14.7 km\textsuperscript{2} based on a section of the map of Helsinki.
%The number of nodes and their communication range vary for different simulations.

There is a total of 160 nodes, 150 of which follow the Working Day Movement Model, and 10 that follow the random waypoint mobility model to simulate vehicles that do not follow daily patterns.
Since this simulation is for vehicles instead of pedestrians, there are no buses in the model and every node is guaranteed to own a vehicle and travel by car.
This configuration was chosen in order to make the network homogenous, but buses and pedestrians could be considered as an addition to the scope.

Aside from the office size parameter, which is 1 in order to inhibit in-office mobility, the parameters regarding offices, meeting spots and shopping were kept intact.
A small part of nodes move randomly to simulate vehicles that do not follow daily patterns.
The transmission range of nodes varies from simulation to simulation, for reasons explained in \Cref{section:density}.

@@

\pagebreak
\Cref{fig:randommalicious1} and \Cref{fig:randommalicious2} show the variation of results for different amounts of malicious nodes in the network.
By the end of one day, the algorithm is able to detect all malicious nodes when they are up to 30\% of the network, although there is still a small amount of false positive detections.
At 40\%, a small part of malicious nodes are yet to be detected and the standard deviation is larger overall.
At 50\%, as expected, the results are inconsistent as the network is completely split between benign and malicious nodes; at this point, the network is considered completely compromised.
True positive and false positive detections are often inverted, because whenever there are more malicious nodes than benign ones in a certain node's network model, the algorithm will classify the malicious ones as correct.
The amount of malicious nodes also affects how quickly nodes are able to acquire information about the network, since nodes do not trust information from malicious neighbors.

### 2018-07-10 dissertation/6-conclusao/chapter6.tex
updated conclusion

%As nodes travel across the network and collect more data from neighbors, they are able to form an abstraction of the network which can be used to detect malicious nodes.
%By placing nodes into strongly connected components, a network containing a large amount of nodes can be simplified into a much smaller one.
%Using a simple graph coloring algorithm, most malicious nodes stand out by having different colors than the majority of nodes.
%This allows for a low complexity approach to malicious node identification in a dynamic network.

@@

In comparison with the related work, TruMan was able to satisfy most of the desired properties for vehicular network trust models, while not inhibiting the properties that were not desired.
Most importantly, TruMan put emphasis on efficiency and is the first model that clearly displays the complexity of its algorithm.

@@

A next step for future work would be performing experiments simulating more types of known attacks against vehicular networks, then adapting the model to resist such attacks.
Furthermore, TruMan could be extended to consider more types of information in its algorithm, using, for example, V2I communications with road-side units, vehicular roles, or location and time parameters.
Finally, the concepts of the algorithm could be applied to different types of networks.

>>>>

As nodes travel across the network and collect more data from neighbors, they are able to form an abstraction of the network which can be used to detect malicious nodes.
By placing nodes into strongly connected components, a network containing a large amount of nodes can be simplified into a much smaller one.
Using a simple graph coloring algorithm, most malicious nodes stand out by having different colors than the majority of nodes.
This allows for a low complexity approach to malicious node identification in a dynamic network.

@@

In comparison with the related work, TruMan was able to satisfy most of the desired properties for vehicular network trust models, while not inhibiting the properties that were not desired.
Most importantly, TruMan put emphasis on efficiency and is the first model that clearly displays the complexity of its algorithm.
Furthermore, TruMan begins taking advantage of social network features found in vehicular networks, although more can be done with this idea.

@@

\pagebreak
Several paths could be considered for future work on TruMan, such as:
\begin{itemize}
\item TruMan could be tested in more varied scenarios, using different maps and various different amounts of nodes in the simulations. It would be even better to use real-world mobility data.
\item TruMan takes advantage of social features found in vehicular networks, but even more could be done with this. For example, vehicles that belong to the same family could have strong ties and share a lot of data with each other. Certain vehicles, such as police cars and ambulances, could have privileged roles within the model.
\item The model could be adapted to include public transportation vehicles (trains, buses) with predictable routes, as well as vehicle-to-infrastructure communication.
\item Well-known vehicular network attacks, such as the ones in \citep{isaac2010security}, could be used against TruMan, attempting to break it. Such experiments would fully validate TruMan's robustness.
\item TruMan should be tested in real-world networks. Although it was designed for vehicular networks, other types of networks with mobility, such as mobile ad-hoc networks, could be used for experiments.
\item Finally, it is possible that TruMan might be a valuable tool for more than just vehicular network. A decentralized and dynamic trust management scheme could be useful for social networks, mobile ad-hoc networks, Internet-based peer-to-peer networks, and others. These scenarios should be tested.
\end{itemize}

%Rede complexas: métricas (dinâmica)? Grafo de Componentes para reduzir a complexidade da rede
%
%Limitações do One? Dtn
%Preservação da rede (slide) mesmo sem alcance da comunicação?
%
%Trust: trusted vehicles (minhas 2010)
%
%Fog computing: cluster em bus stops ou rsup
%
%Contribuição: correção & eficiência, redes sociais wdmm, rotina,
%
%Janela de tempo para descoberta e atualização dinâmica da topologia- execução dos 3 passos seguintes (limitação do tempo - iteração?) alguma frequência ? F(v, d)
%M ? 
%
%
%Diagnóstico (ok - fora do escopo) - sem análise do teste do nó.
%
%Noticias boas mais rápido que más: retirada da aresta?
%Modelo de ataques?
